Overlapping Batches for the Assessment of Solution Quality in Stochastic Programs

### 2014-05-21 Referee1_Response.tex

\documentclass[11pt,notitlepage,onecolumn]{article}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{makeidx}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{chicago}
\usepackage[singlespacing]{setspace}

\setcounter{MaxMatrixCols}{10}

\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}

\newcommand{\noi}{\noindent}

\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\singlespacing

\baselineskip0.26in

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\pagebreak

\begin{center}
\textbf{\Large Response to Referee 1} 
\medskip

{\large Overlapping Batches for the Assessment of Solution Quality in Stochastic Programs}
\medskip

{\footnotesize by D. Love and G. Bayraksan}
\end{center}

\bigskip

\bigskip

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

We thank the referee for the helpful comments and suggestions. 
We incorporated all of the recommended changes and believe the paper is improved as a result. 
Below, we go through in detail these changes. 
\medskip

\bigskip

%%%%%%%%%%%%%%%%%
%% Need to be careful with the minor changes. Will these be affected?
%% Need to CHECK AT THE VERY END... FOR ANY CHANGES on TOP OF these...
%%    - GB
%%%%%%%%%%%%%%%%%

\noi  
{\large \bf ``Major'' comments:}
\medskip

\begin{itemize}
\item[\textbf{M1.}] \textit{In the typical simulation setting, the computational effort required to produce the output dominates, and hence one would like to ``make the most'' of the output in terms of analysis. 
Sometimes, a similar motivation can arise in stochastic optimization because there may be a computationally expensive underlying simulation model that must be run to produce the i.i.d.\ realizations that are then used in an SAA approach. 
(While they don't now, the authors could include this as motivation for
their work.)}
\end{itemize}

\noi 
We thank the referee for this suggestion. 
You are right.
There are cases when generating scenarios is expensive in the stochastic optimization setting as well. 
We changed the introduction based on your, the associate editor and the other reviewer's comments. 
We specifically added this as a motivation. 
\medskip

\begin{itemize}
\item[] \textit{However, perhaps more often, sampling the i.i.d. realizations is computationally cheap compared to solving the resulting SAA instances in stochastic optimization. 
In this latter case, we have a choice between simply increasing the number of batches in a non-overlapping method or using the overlapping batch means approach (with some degree of overlap) in order to reduce variance.
Based on the paper's results, perhaps the computational effort required to achieve a level of variance reduction should guide this choice. 
The authors do point to the fact that warm starts in a stochastic
optimization algorithm can be exploited much more easily when using overlapping batch means than when not using overlapping batches. 
Some attempt to explore this tradeoff would be valuable. 
The computational results use sorting (for the news vendor problem), a dynamic programming algorithm (for a stochastic knapsack model), and a decomposition method (for two-stage stochastic linear programs). 
While I am not suggesting that this exploration needs to be made for all three types of algorithms, even exploring it in the case of the sorting algorithm (where some algorithms are well suited for almost-sorted lists) could provide valuable insight.}
\end{itemize}

\noi 
xxx Need to discuss xxx  \medskip 
We performed such an analysis and provide the results of this in the new subsection 7.4... ?? 
Etc.
\medskip

\begin{itemize}
\item[\textbf{M2.}] \textit{The choice of the lower bound that is embedded in equation (8) is interesting. 
(The upper bound in equation (8) is completely natural as the sample mean of the $n_l$ realizations of the function evaluated at $\hat{x}$.) 
It seems that there are also other natural choices that could be made here for the lower bound. 
There is some discussion of this choice in the text that follows equations (7)-(9), but can the authors say more? For example, do the consistency and asymptotic validity results that follow hinge on this choice? Or, do those results also hold for other choices, like forming $\bar\bar{G}$ as a sample
mean of the underlying $\bar{G}$ values. 
We know that the individual gap estimators in (7) are nonnegative, and if we formed $\bar\bar{G}$ as a sample mean of $\bar{G}$ values, it would be nonnegative. 
Is the $\bar\bar{G}$, as specified in (8), nonnegative? 
Have the authors computationally explored other choices here? 
Any insight in this vein would be valuable to the reader in understanding the choice made in equation (8).}
\end{itemize}

\noi
xxxx  Need to discuss. 
I know I changed this but I don't remember why at this point. 
Some theory was incorrect but at that time, we had more relaxed conditions. 
Now we have exponential rates of convergence and it seems to me like anything here should be fine. 
I haven't checked but pretty sure. 
So, yes, why don't we use something else? 
When we did, the results weren't that different at all. 
Right?\ \ \ \ 
xxxxx
\medskip

\bigskip

\noi {\large \bf Minor comments:}

\bigskip

\begin{itemize}
\item[1.] \textit{p1, l49: Suggest: The Overlapping \ldots }
\end{itemize}

\noindent xxx Done. 
\medskip

\begin{itemize}
\item[2.] \textit{p2, l16, l22: overlapping is misspelled twice.}
\end{itemize}

\noindent xxx Corrected. 
\medskip

\begin{itemize}
\item[3.] \textit{p3, l23: Do the authors mean ``relaxations'' rather than ``relations''?}
\end{itemize}

\noindent xxx Corrected. 
\medskip

\begin{itemize}
\item[4.] \textit{p3, l38: Suggest: estimator of the optimality gap \ldots}
\end{itemize}

\noindent xxx Changed. 
\medskip

\begin{itemize}
\item[5.] \textit{p4, l34: Suggest: once the data are generated through a simulation, they \ldots}
\end{itemize}

\noindent xxx Changed. 
\medskip

\begin{itemize}
\item[6.] \textit{p4, l42: Suggest: Partial overlap results in fewer batches, hence fewer optimization \ldots}
\end{itemize}

\noindent xxx Changed. xxx MUST CHECK WITH OTHER REFEREE'S COMMENTS.
\medskip

\begin{itemize}
\item[7.] \textit{p6, l32: Suggest: The degrees \ldots make \ldots}
\end{itemize}

\noindent xxx Changed. 
\medskip

\begin{itemize}
\item[8.] \textit{p7, l18: While a confidence level of $1-\alpha$ may be consistent with a level of significance of $\alpha$, perhaps this could be reworded (as it seemed to distract this reader a bit).}
\end{itemize}

\noindent xxx Changed the wording here. 
Thank you. 
\medskip

\begin{itemize}
\item[9.] \textit{p10, l23: Suggest: convergence of the sampled solution \ldots}
\end{itemize}

\noindent xxx Changed. 
\medskip

\begin{itemize}
\item[10.] \textit{p12, l53: Suggest: Strong consistency \ldots has been \ldots}
\end{itemize}

\noindent xxx Changed. 
\medskip

\begin{itemize}
\item[11.] \textit{p14, l13-14: Suggest: The fringe batches come \ldots The first and last batch are identically \ldots}
\end{itemize}

\noindent xxx Changed. 
\medskip

\begin{itemize}
\item[12.] \textit{ p14, l23: Please add $j = 1$ to the sum.}
\end{itemize}

\noindent xxx Added. 
\medskip

\begin{itemize}
\item[13.] \textit{p14, l35: The authors have gone to some length to distinguish different types of $A_j$ terms.
However, this equation has an $\mathbb{E}A_j^2$ term that has been collapsed from a sum, but we don't know ``which $j$''. 
Should there be a $\max_j \mathbb{E}A_j^2$ or some other treatment here?}
\end{itemize}

\noindent xxx NEED TO CHECK AND CORRECT AS NECESSARY. 
\medskip

\begin{itemize}
\item[14.] \textit{p15, Theorem 3: A hypothesis in the theorem is that $\hat{x} \neq x^*$, and yet the proof starts with the case that $\hat{x} = x^*$. 
That hypothesis could be removed if the claim had a ``$\geq$'' or this statement could be removed or modified.}
\end{itemize}

\noindent Thank you for catching this.  
We removed this statement from the proof of Theorem 3 and added it as a remark in the paragraph after the theorem.
\medskip

\begin{itemize}
\item[15.] \textit{p17, l44: Suggest: A summary of results \ldots experiments is depicted \ldots}
\end{itemize}

\noindent Done.
%\ \ \ XXXX CHECK LATER: THIS SECTION MIGHT CHANGE. 
\medskip

\begin{itemize}
\item[16.] \textit{p17, l55: Perhaps add a comment on why DB1 may not experience the asymptotic variance reduction? 
(Is it because it may lack a unique solution?)}
\end{itemize}

\noindent
Done.
% xxx Yes, it is partially because we are not sure if it has a unique optimal solution as DB1 has never been solved before. 
%Even if it has been solved, the variance reduction is shown asymptotically but the computations are only for small sample sizes. 
%We reworded this to reflect these points.
%Thank you for this suggestion. 
\medskip

\begin{itemize}
\item[17.] \textit{p18, figures: The figures are a bit small and hence can be hard to read without enlarging them (but perhaps this will be taken care of at production).}
\end{itemize}

\noindent xxx We enlarged the figures. 
\medskip

\begin{itemize}
\item[18.] \textit{p18, l57: The authors speak of coverage probabilities for DB1, but how can this be done without knowing an optimal solution to DB1?}
\end{itemize}

\noindent 
We used a Latin hypercube sample of size 50,000 estimate $\mu_{\hat{x}}$ for DB1, which was then used to estimate the coverage probability of the OMRP CIs for this test problem.
We explain this at the end of Section 5.1 (Test Problems). 
We also changed the wording in Section 5.3 (Results of Experiments) to make it clear that the coverage probability is estimated for the test problem DB1. 
\medskip

\begin{itemize}
\item[19.] \textit{p19: It may be possible to expand on the last paragraph of Section 5, in giving guidance on selecting the degree of overlap, depending on the authors' response to comment M1 above.}
\end{itemize}

\noindent xxx We expanded this paragraph based on our findings. 
xxx Write more---hopefully, we will find good stuff!!!
\medskip

\end{document}

### 2014-05-21 Referee2_Response.tex

\documentclass[11pt,notitlepage,onecolumn]{article}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{makeidx}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{chicago}
\usepackage[singlespacing]{setspace}

\setcounter{MaxMatrixCols}{10}

\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}

\newcommand{\noi}{\noindent}

\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\singlespacing

\baselineskip0.26in

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\pagebreak

\
\begin{center}
\textbf{\Large Response to Referee 2} 
\medskip

{\large Overlapping Batches for the Assessment of Solution Quality in Stochastic Programs}
\medskip

{\footnotesize by D. Love and G. Bayraksan}
\end{center}

\bigskip

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

We thank the referee for the helpful comments and suggestions. 
We incorporated all of the recommended changes and believe the paper is improved as a result. 
Below, we go through in detail these changes. 
\medskip

\bigskip

%%%%%%%%%%%%%%%%%
%% Need to be careful with the minor changes. Will these be affected?
%% Need to CHECK AT THE VERY END... FOR ANY CHANGES on TOP OF these...
%%    - GB
%%%%%%%%%%%%%%%%%

\noi  
{\large \bf General Comments:}
\medskip

\begin{itemize}
\item[1.] \textit{The main contributions of the paper need to be stated more clearly and succinctly.}
\end{itemize}

\noindent 
xxx  We agree. 
We changed the introduction to clearly state the contributions of the paper and \ldots 
\medskip

\begin{itemize}
\item[2.] \textit{It is not necessary to go into such detail in the OBM review.}
\end{itemize}

\noindent 
xxx  We shortened the section on OBM review by combining \ldots 
\medskip

\begin{itemize}
\item[3.] \textit{The English needs to be tightened up somewhat.}
\end{itemize}

\noindent  
xxxx
You are right. 
We went through the paper and tightened up the prose. 
We also incorporated all the changes you suggested below and hope the exposition of the paper is improved as a result.
We hope that any remaining English issues could be corrected by the English editor of the journal. (IS THERE ONE????) 
xxxx
\medskip

\bigskip

\noi  
{\large \bf Specific Comments:}
\medskip

\begin{itemize}
\item[] \textit{Page 1, Line 32 (and elsewhere): I believe that you ``apply the OBM method to stochastic programming'' rather than extend it.}
\end{itemize}

\noi
xxx  I actually prefer 'extend' but I am not going to argue over such small stuff. 
So, I will change this sentence and might look for others. 
\medskip

\begin{itemize}
\item[] \textit{1, 35 (and elsewhere): ``We give conditions'' instead of ``We show conditions''}
\end{itemize}

\noi
xxx  Changed
\medskip

\begin{itemize}
\item[] \textit{1, 37: What are the classical results? Reference?}
\end{itemize}

\noi
xxx  
\medskip

\begin{itemize}
\item[] \textit{1, 49: Suggested rewrite to reduce ambiguity: ``The overlapping batch means (OBM) \ldots to obtain variance estimators having variances that are comparatively lower than their nonoverlapped counterparts. 
In the context of steady-state simulation, OBM is often used to estimate the variance of the sample mean, which is itself an estimator for the mean. 
Schmeiser et al.\ [1990] use overlapping estimators to estimate the
variance of estimators for non-means. 
More recently, overlapping estimators based on standardized time series (as opposed to batch means) have been evaluated [Alexopoulos et al., 2007a,b].'' 
In this rewrite, note the use of active and passive referencing formats.}
\end{itemize}

\noi
xxxx  Thank you for this suggestion of rewrite. 
We rewrote this paragraph based on your corrections and paying attention to referencing formats. 
\medskip

\begin{itemize}
\item[] \textit{2, 5: ``never before been studied . . . context.''}
\end{itemize}

\noi
xxx  Changed.
\medskip

\begin{itemize}
\item[] \textit{2, 7: By ``same benefits'', you mean moderate bias and comparatively low variance, right?}
\end{itemize}

\noi
xxx  
\medskip

\begin{itemize}
\item[] \textit{2, 8: Start a new paragraph with ``A natural setting\ldots ''.}
\end{itemize}

\noi
xxx  
\medskip

\begin{itemize}
\item[] \textit{2, 10: ``especially'' instead of ``esp.''. 
Also, ``This'' instead of ``Assessing solution quality in stochastic programming'' (since it's repetitive)}
\end{itemize}

\noi
xxx  
\medskip

\begin{itemize}
\item[] \textit{2, 13: ``Because optimality gap''}
\end{itemize}

\noi
xxx  
\medskip

\begin{itemize}
\item[] \textit{2, 24: ``under which the resulting gap estimators exhibit reduced variance when compared to their counterparts obtained via nonoverlapping batches.''}
\end{itemize}

\noi
xxx  
\medskip

\begin{itemize}
\item[] \textit{2, 24 (and elsewhere): Note: I would be careful about the use of the term ``variance reduction'', which usually refers to the class of techniques such as common random numbers, antithetics, importance sampling, etc. 
I view what you're doing in this paper as simply proposing a new estimator whose variance is lower than that of a competing estimator.}
\end{itemize}

\noi
xxx  You are right. 
Thanks for pointing this out. We corrected the wording throughout the paper. 
\medskip

\begin{itemize}
\item[] \textit{2, 27: ``and that the interval \ldots valid. 
We also present''}
\end{itemize}

\noi
xxx  
\medskip

\begin{itemize}
\item[] \textit{2, 28: ``Our experiments indicate that the use of overlapping estimators results in gap estimators achieving lower variance than their nonoverlapping counterparts, along with comparable bias and interval coverage --- for both small- and large-sample cases.}
\end{itemize}

\noi
xxx  
\medskip

\begin{itemize}
\item[] \textit{2, 34 (and elsewhere): Might want to boldface all vectors.}
\end{itemize}

\noi
xxx  
\medskip

\begin{itemize}
\item[] \textit{2, 42 (and elsewhere): ``more-restrictive moment'' (hyphenate certain non-adverbial compound adjectives)}
\end{itemize}

\noi
xxx  Thank you; we went through the paper and hyphenated all the compound adjectives.
\medskip

\begin{itemize}
\item[] \textit{2, 51: You can delete ``(SAA)'', since the notation isn't used again in the paper.}
\end{itemize}

\noi
xxx  
\medskip

\begin{itemize}
\item[] \textit{3, 11: ``solution; and''}
\end{itemize}

\noi
xxx  
\medskip

\begin{itemize}
\item[] \textit{3, 24 (and elsewhere): ``Lagrangian, or'' (comma after penultimate entry in a conjunctive list)}
\end{itemize}

\noi
xxx  
\medskip

\begin{itemize}
\item[] \textit{3, 37: ``we can simply use $z_m^*$''}
\end{itemize}

\noi
xxx  
\medskip

\begin{itemize}
\item[] \textit{3, 38: ``estimator of the optimality''}
\end{itemize}

\noi
xxx  
\medskip

\begin{itemize}
\item[] \textit{3, 53: ``The sample variance of these estimators is used to form confidence intervals for the optimality gap (we further review MRP in \S 2.2).''}
\end{itemize}

\noi
xxx  
\medskip

\begin{itemize}
\item[] \textit{4, 5 (and elsewhere): ``see, e.g., Bertocchi et al. [2000]; \ldots ''}
\end{itemize}

\noi
xxx  I don't think I agree with this. 
These need to be in parentheses! 
\medskip

\begin{itemize}
\item[] \textit{4, 14: Delete the sentence ``Especially \ldots '' since it doesn't really add anything to the discussion.}
\end{itemize}

\noi
xxx  Deleted.
\medskip

\begin{itemize}
\item[] \textit{4, 17: ``interest is that of estimating''}
\end{itemize}

\noi
xxx  
\medskip

\begin{itemize}
\item[] \textit{4, 20--27: Even though I believe everything, these lines are a bit awkward and confusing.}
\end{itemize}

\noi
xxx   DAVID-- NEED YOUR HELP with this. 
I don't know how to reword it to make it less awkward.
\medskip

\begin{itemize}
\item[] \textit{4, 31: What are the desired statistical properties?}
\end{itemize}

\noi
xxx  
\medskip

\begin{itemize}
\item[] \textit{4, 33: ``Another difference is that''. By the way, what is ``difference'' referring to?}
\end{itemize}

\noi
xxx  
\medskip

\begin{itemize}
\item[] \textit{4, 36: ``due to the need to solve sampling problem"}
\end{itemize}

\noi
xxx  
\medskip

\begin{itemize}
\item[] \textit{4, 42: ``Partial overlapping results in a smaller number of batches; hence, fewer optimization''}
\end{itemize}

\noi
xxx  
\medskip

\begin{itemize}
\item[] \textit{4, 45: The sentence ``Second, \ldots '' needs some clarification, since it states a conclusion that hasn't so far been justified.}
\end{itemize}

\noi
xxx  
\medskip

\begin{itemize}
\item[] \textit{4, 51: ``discuss overlapping''}
\end{itemize}

\noi
xxx  
\medskip

\begin{itemize}
\item[] \textit{4, 54 (and elsewhere): When you refer to ``variable amounts of overlap'', that is really nothing new. Certainly, any overlapping estimator will have end effects in which the overlap amounts differ from those in the ``middle'' region of the data.}
\end{itemize}

\noi
xxx  
\medskip

\begin{itemize}
\item[] \textit{4, 57 (and elsewhere): ``classical case'' refers to nonoverlapping batch means, right?}
\end{itemize}

\noi
xxx  Yes. 
We reworded this sentence to make it clear.
\medskip

\begin{itemize}
\item[] \textit{5, 12: Does $\sigma^2$ refer to the marginal variance or the ``variance parameter'' (sum of the covariances at all lags)?}
\end{itemize}

\noi
xxx   CHECK -- DON'T REMEMBER
\medskip

\begin{itemize}
\item[] \textit{5, 14: ``realization of the univariate stochastic''}
\end{itemize}

\noi
xxx  
\medskip

\begin{itemize}
\item[] \textit{5, 35 (and elsewhere): Careful! This isn't quite the sample variance! This is actually the sample variance multiplied by $m/n$.}
\end{itemize}

\noi
xxx  Thanks for catching this! We corrected this and others.
\medskip

\begin{itemize}
\item[] \textit{5, 43: You could have introduced the notation ``CI'' earlier.}
\end{itemize}

\noi
xxx  You are right. 
We now do introduce it earlier in the paper -- GIVE PAGE NO.
\medskip

\begin{itemize}
\item[] \textit{5: You can significantly reduce the discussion on OBM here and in \S 3.1. 
Just let the reader know the main results that you'll use.}
\end{itemize}

\noi
xxx  
\medskip

\begin{itemize}
\item[] \textit{6, 13: ``corresponding overlapping batch means''}
\end{itemize}

\noi
xxx  
\medskip

\begin{itemize}
\item[] \textit{6, 29: Note that you use ``Note that'' too often.}
\end{itemize}

\noi
xxx  
\medskip

\begin{itemize}
\item[] \textit{6, 30: Explicitly say what the d.f.\ in (2) is.}
\end{itemize}

\noi
xxx  
\medskip

\begin{itemize}
\item[] \textit{7, 46: Does $\gamma$ need to be an integer? 
You seem to be using it that way, so maybe state the requirement.}
\end{itemize}

\noi
xxx  CHECK THIS
\medskip

\begin{itemize}
\item[] \textit{8, 4 (and elsewhere): Define notations such as floor and ceiling functions.}
\end{itemize}

\noi
xxx  
\medskip

\begin{itemize}
\item[] \textit{8, 11: In addition to the fact that I don't think ``variance reduction'' is quite the right term, the phrase ``variance reduction in this estimator'' is awkward.}
\end{itemize}

\noi
xxx  
\medskip

\begin{itemize}
\item[] \textit{8, 53--57: The various OBM references should have been discussed earlier.}
\end{itemize}

\noi
xxx  
\medskip

\begin{itemize}
\item[] \textit{10, 11 (and elsewhere): ``$E[f(x, \xi)^4]$'' instead of ``$Ef(x, \xi)^4$'' (never hurts to use some brackets to reduce ambiguity)}
\end{itemize}

\noi
xxx Changed. 
\medskip

\begin{itemize}
\item[] \textit{11, 33: It might be helpful to add a step before the first inequality in the proof.}
\end{itemize}

\noi
xxx  
\medskip

\begin{itemize}
\item[] \textit{12, 52: ``$n_l VD_l$' has been studied''}
\end{itemize}

\noi
xxx  
\medskip

\begin{itemize}
\item[] \textit{13, 12 (and elsewhere): I may have missed this, but has the notation $\sigma_{\hat{x}}$ been established yet? 
In any case, some of the verbiage in this paragraph is a bit repetitive.}
\end{itemize}

\noi
xxx  
\medskip

\begin{itemize}
\item[] \textit{13, 44: Is the expression for d.f. too big?}
\end{itemize}

\noi
xxx  
\medskip

\begin{itemize}
\item[] \textit{13, 53: The reader might need another step besides C-S to get that inequality.}
\end{itemize}

\noi
xxx  
\medskip

\begin{itemize}
\item[] \textit{15, 25: Do you discuss $t_{d_l,\alpha}$ at all in Theorem 3?}
\end{itemize}

\noi
xxx  CHECK. DON'T RECALL.
\medskip

\begin{itemize}
\item[] \textit{18: Your figures are very difficult to read, even with the pdf file.}
\end{itemize}

\noi
xxx  
\medskip

\begin{itemize}
\item[] \textit{20, 47: ``4th edition''}
\end{itemize}

\noi
Done.
\medskip

\begin{itemize}
\item[] \textit{21, 23: ``\it Jackknife''}
\end{itemize}

\noi
Corrected. Thank you.

\end{document}

### 2014-05-21 omrp_lb_rev.tex
Added .tex files for the revision
1. omrp_lb_rev.tex (revised paper)
2. EinC_response.tex
3. AE response
4. Referee1 response
5. Referee2 response
and 6. the .bib file

\begin{proof}
	Note that for $\xh = \xs$, $\lim_{l\rightarrow\infty} \p{\mu_\xh \leq I^G_l} = 1$.  
        With $\xh \neq \xs$, let $X_l = \frac{\dbb_l - \mu_\xh}{\sigma^2_\xh/\sqrt{n_l}}$, $Y_l = \frac{\gbb_l - \mu_\xh}{\sigma^2_\xh/\sqrt{n_l}}$, and $Z_l = \frac{\sigma^2_\xh}{\sqrt{n_lVD_l}} \frac{\sqrt{n_lVD_l}}{\sqrt{n_lVG_l}}$.  
        It is suffices to show $Y_lZ_l = \frac{\gbb_l - \mu_\xh}{\sqrt{VG_l}} \Rightarrow N(0,1)$, where $\Rightarrow$ denotes convergence in distribution.  
        First, we show that $|X_l - Y_l| \rightarrow 0$, a.s.  Note that $|X_l - Y_l| > 0$ if and only if $|\dbb_l - \gbb_l| > 0$.  
        In the proof of Theorem \ref{thm:strong_consistency} we showed that $\left\{ \dbb_l - \gbb_l \neq 0 \right\}$ happens only finitely many times, so $|X_l - Y_l| \rightarrow 0$, a.s.\ by the Borel-Cantelli Lemma. 
        Next, since $X_l \Rightarrow N(0,1)$  by the central limit theorem and $|X_l - Y_l| \rightarrow 0$ in probability, $Y_l \Rightarrow N(0,1)$.  
        By hypothesis and Theorem \ref{thm:strong_consistency}, $Z_l \rightarrow 1$ in probability.  
        Thus, by Slutsky's theorem, $Y_lZ_l \Rightarrow N(0,1)$.
\end{proof}

The asymptotic validity of the OMRP confidence interval requires $n_l VD_l$ to converge in probability to $\sigma^{2}_{\xh}$. 
This can be achieved either by almost sure or mean-square convergence, which gives a larger range of $r$ in the batching structure.

@@

The candidate solutions used for NVD and CEP1 and their characteristics can be found in \citep{Bayraksan2006}.
We used the candidate solution (0, 0, 1, 1, 1, 0, 1, 1, 0, 1) for 10D with $\mu_{\xh} = 158.579$ and the candidate solution (11, 14, 8, 11, 7) for DB1 with an estimated $\mu_{\xh} = 1.08$. 
Because the optimal solution of DB1 is unknown, a Latin hypercube sample of size 50,000 was used to estimate $\mu_{\xh}$, which was then used below to estimate the coverage probability of the OMRP CIs for this test problem.

@@

Summary of results from these experiments are depicted in Figures~\ref{fig:nv} and \ref{fig:varvar}.
Figures~\ref{fig:nv}(a) and \ref{fig:varvar} show the reduction of variance, with each term being normalized with respect to $\var{nVG}$ of the nonoverlapping case (MRP). 
The solid lines in these figures show the theoretical variance reduction from \citep{Welch1987} given by (\ref{eq:var_reduct_formula}). 
Empirical results agree with the theoretical values well, with more variability observed in CEP1, 10D, and DB1. 
These experiments suggest that similar variance reduction can be achieved in stochastic programming by overlapping the batches, even with small sample sizes.
We note that the variance reduction in DB1 can be less than the asymptotic amount. %for the small sample sizes used in these experiments. 
Even with the relatively small sample sizes compared to the size of this problem, however, overlapping appears to achieve some variance reduction.

@@

Finally, Figure~\ref{fig:nv}(c) shows the coverage probability of confidence intervals generated by OMRP for several values of $m$ across varying values of $\gamma/m$ for the newsvendor problem.  
The results of the classical overlapping batches estimators show that coverage probability does not change with the amount of overlap, which we can  empirically see in this figure for OMRP for NVD.
We observed the same for CEP1, 10D, and DB1.  
The coverage probabilities from applying the (nonoverlapping) MRP algorithm to these problems presented in \citep{Bayraksan2006} agree with our results: for the newsvendor problem, coverage probability drops as $m$ increases and the coverage probability of CEP1 (not shown) remains fairly constant around the desired value of $90\%$. 
Coverage probability for 10D and DB1 (not shown) were very high, more than $0.99$.  
The bias from solving (\ref{eq:sto_prog_m}) for these problems seems to be much more significant than the variance.

@@

% \section*{AUTHOR BIOGRAPHIES}

% \noindent {\bf DAVID LOVE} is a graduate student in the Inderdisciplinary Program in Applied Mathematics at the University of Arizona.  His research focuses on Monte Carlo based quality assessment in stochastic programming.  His email address is \href{mailto://dlove@email.arizona.edu}{dlove@email.arizona.edu}.\\

% \noindent {\bf G\"{U}Z\.{I}N BAYRAKSAN} is an Assistant Professor in the Department of Systems and Industrial Engineering at the University of Arizona. Her research interests include stochastic optimization, particularly Monte Carlo sampling-based methods for stochastic programming, with applications to water resources management. Her email address is \href{mailto://guzinb@sie.arizona.edu}{guzinb@sie.arizona.edu} and her web page is \href{http://www.sie.arizona.edu/faculty/guzinb}{www.sie.arizona.edu/faculty/guzinb}.\\

>>>>

\begin{proof} 
%        With $\xh \neq \xs$, 
			Let $X_l = \frac{\dbb_l - \mu_\xh}{\sigma^2_\xh/\sqrt{n_l}}$, $Y_l = \frac{\gbb_l - \mu_\xh}{\sigma^2_\xh/\sqrt{n_l}}$, and $Z_l = \frac{\sigma^2_\xh}{\sqrt{n_lVD_l}} \frac{\sqrt{n_lVD_l}}{\sqrt{n_lVG_l}}$.  
        It is suffices to show $Y_lZ_l = \frac{\gbb_l - \mu_\xh}{\sqrt{VG_l}} \Rightarrow N(0,1)$, where $\Rightarrow$ denotes convergence in distribution.  
        First, we show that $|X_l - Y_l| \rightarrow 0$, a.s.  Note that $|X_l - Y_l| > 0$ if and only if $|\dbb_l - \gbb_l| > 0$.  
        In the proof of Theorem \ref{thm:strong_consistency} we showed that $\left\{ \dbb_l - \gbb_l \neq 0 \right\}$ happens only finitely many times, so $|X_l - Y_l| \rightarrow 0$, a.s.\ by the Borel-Cantelli Lemma. 
        Next, since $X_l \Rightarrow N(0,1)$  by the central limit theorem and $|X_l - Y_l| \rightarrow 0$ in probability, $Y_l \Rightarrow N(0,1)$.  
        By hypothesis and Theorem \ref{thm:strong_consistency}, $Z_l \rightarrow 1$ in probability.  
        Thus, by Slutsky's theorem, $Y_lZ_l \Rightarrow N(0,1)$.
\end{proof}

The asymptotic validity of the OMRP confidence interval requires $n_l VD_l$ to converge in probability to $\sigma^{2}_{\xh}$. 
This can be achieved either by almost sure or mean-square convergence, which gives a larger range of $r$ in the batching structure.
Also, a hypothesis of Theorem~\ref{thm:conf_int} is that $\xh \neq \xs$.  For $\xh = \xs$, we have $\lim_{l\rightarrow\infty} \p{\mu_\xh \leq I^G_l} = 1$.

@@

The candidate solutions used for NVD and CEP1 and their characteristics can be found in \citep{Bayraksan2006}.
We used the candidate solution (0, 0, 1, 1, 1, 0, 1, 1, 0, 1) for 10D with $\mu_{\xh} = 158.579$ and the candidate solution (11, 14, 8, 11, 7) for DB1 with an {\it estimated} $\mu_{\xh} = 1.08$. 
Because the optimal solution of DB1 is unknown, a Latin hypercube sample of size 50,000 was used to estimate $\mu_{\xh}$, which was then used below to estimate the coverage probability of the OMRP CIs for this test problem.

@@

A summary of results from these experiments is depicted in Figures~\ref{fig:nv} and \ref{fig:varvar}.
Figures~\ref{fig:nv}(a) and \ref{fig:varvar} show the reduction of variance, with each term being normalized with respect to $\var{nVG}$ of the nonoverlapping case (MRP). 
The solid lines in these figures show the theoretical variance reduction from \citep{Welch1987} given by (\ref{eq:var_reduct_formula}). 
Empirical results agree with the theoretical values well, with more variability observed in CEP1, 10D, and DB1. 
These experiments suggest that similar variance reduction can be achieved in stochastic programming by overlapping the batches, even with small sample sizes.
We note that the variance reduction in DB1 can be less than the asymptotic amount. %for the small sample sizes used in these experiments. 
Due its size, DB1 has not yet been solved to optimality, therefore, it may lack a unique optimal solution. 
Even with the relatively small sample sizes compared to the size of this problem, however, overlapping appears to achieve some variance reduction.

@@

Finally, Figure~\ref{fig:nv}(c) shows the coverage probability of confidence intervals generated by OMRP for several values of $m$ across varying values of $\gamma/m$ for the newsvendor problem.  
The results of the classical overlapping batches estimators show that coverage probability does not change with the amount of overlap, which we can  empirically see in this figure for OMRP for NVD.
We observed the same for CEP1, 10D, and DB1.  
The coverage probabilities from applying the (nonoverlapping) MRP algorithm to these problems presented in \citep{Bayraksan2006} agree with our results: for the newsvendor problem, coverage probability drops as $m$ increases and the coverage probability of CEP1 (not shown) remains fairly constant around the desired value of $90\%$. 
Coverage probability for 10D (not shown) and {\it estimated} coverage probability for DB1 (also not shown) were very high, more than $0.99$.  
The bias from solving (\ref{eq:sto_prog_m}) for these problems seems to be much more significant than the variance.

@@
